# Network Connectivity

Note that actual code is loaded from a different file.

```{r external-code, cache=FALSE}
read_chunk('03_network_connectivity.R')
```


## Setup

```{r general-setup, messages='hide', results='hide'}
```

```{r network-setup}
```

### Read in Data

```{r phenotypes}
```

```{r timeseries}
```

Note since analyses will focus on the default-mode network and the task positive networks, time-series will be restricted to only those networks.


## Connectivity

For each subject, calculate the correlation between the DMN time-series and each of 3 TP time-series.

```{r connectivity}
```

### Distribution

```{r connectivity-distribution}
```


## Brain-Behavior

Generally the approach below is to examine the relationship between each phenotypic measure and DMN/TP network connectivity via scatter plots and a table of Z-Scores assessing the significance of the relationships.

### Needed Functions

```{r brain-behavior-functions}
```

### For Each Total Score

```{r brain-behavior-totals, fig.width=8, fig.height=4, results='asis'}
```

### For SIPI SubScale

```{r brain-behavior-sipi}
```

### For RRS SubScale

```{r brain-behavior-rrs}
```

### For PANAS SubScale

```{r brain-behavior-panas}
```

