# Associations between MSIT-DMN and DN-TP connectivity

Note that actual code is loaded from a different file.

```{r external-code, cache=FALSE}
read_chunk('05_connectivity_vs_msit.R')
```

## Overview

Only the connectivity between DN and Right Frontoparietal is marginally related to MSIT-DN correlation. 

## Setup

```{r general-setup, message=FALSE, results='hide'}
```

```{r network-setup}
```

Read in subject information.

```{r subject-info}
```

Get the incoherent > coherent predicted task signal together.

```{r task-waver, fig.width=8, fig.height=4}
```

Read in the time-series data.

```{r msit-ts}
```

## Pre-Analysis Calculations

Get the correlation (Fischer Z transformed) between the MSIT predicted task signal and the DMN signal. For each subject, collapse this measure across scans/runs (i.e., get the mean). Note that this time, I have flipped the MSIT task to DMN signal correlation so it is generally negative.

```{r msit-dmn-correlation, fig.width=8, fig.height=4}
```

Get the connectivity between the DN and TP networks at rest. For each subject, collapse this measure across scans/runs (i.e., get the mean).

```{r connectivity}
```

```{r combine}
```

## Plot and Significate

```{r functions}
```

Ugh, not significant.

```{r signif}
```

Plot doesn't look good either.

```{r plots, fig.width=12, fig.height=4}
```
