# Associations between MSIT-DMN and Rest-DMN-Kurtosis

Note that actual code is loaded from a different file.

```{r external-code, cache=FALSE}
read_chunk('05_kurtosis_vs_msit.R')
```

## Setup

```{r general-setup, message=FALSE, results='hide'}
```

```{r network-setup}
```

Read in subject information.

```{r subject-info}
```

Get the incoherent > coherent predicted task signal together.

```{r task-waver}
```

Read in the time-series data.

```{r msit-ts}
```

## Pre-Analysis Calculations

Get the correlation (Fischer Z transformed) between the MSIT predicted task signal and the DMN signal. For each subject, collapse this measure across scans/runs (i.e., get the mean). Note that this time, I have flipped the MSIT task to DMN signal correlation so it is generally negative.

```{r msit-dmn-correlation}
```

Get the kurtosis of the DMN signal at rest. For each subject, collapse this measure across scans/runs (i.e., get the mean).

```{r kurtosis}
```

Make some plots of these 2 measures.

```{r combine}
```

## Plot and Significate

```{r comparison-functions}
```

Ugh, not significant.

```{r comparison-signif}
```

Plot doesn't look good either. 

```{r comparison-plot}
```
