# RT-based Associations

Note that actual code is loaded from a different file.

```{r external-code, cache=FALSE}
read_chunk('06_rt_stuff.R')
```

## Overview

Not much to see here :(.

* Connectivity between DN and Executive Control network was significantly related to mean RT across both coherent and incoherent trials.
* Connectivity between DN and Left Frontoparietal network was significantly related to RT CV for incoherent trials (and p=0.1 for coherent trials).
* AIM was positively related to mean RT for coherent and incoherent trials.
* RRS as well as all most of its subscales were positively related to RT CV for coherent and incoherent trials.
* BDI was positively related to mean RT for incoherent trials.
* PANAS negative was positively related to mean RT for incoherent trials.
* PANAS positive was positively related to RT CV for incoherent trials.

## Setup

```{r general-setup, message=FALSE, results='hide'}
```

```{r network-setup}
```

```{r subject-info}
```

```{r rts}
```

```{r task-waver}
```

```{r timeseries}
```

## Calculate measures

```{r rts-summarize, message=FALSE}
```

```{r kurtosis, message=FALSE}
```

The CCD seems to be slightly positively shifted in its distribution. I hope this is not due to differences in any preprocessing steps.

```{r connectivity, message=FALSE}
```

```{r msit-dmn-correlation, message=FALSE}
```

```{r combine}
```

## Assocations between RT and brain measures

```{r fone}
```

### DN Kurtosis

```{r kurtosis-meanrt, fig.width=8, fig.height=4}
```

```{r kurtosis-cvrt, fig.width=8, fig.height=4}
```

### TP-DN Connectivity

```{r connectivity-meanrt, fig.width=8, fig.height=6}
```

```{r connectivity-cvrt, fig.width=8, fig.height=6}
```

### MSIT-DN Correlation

```{r msit_dn-meanrt, fig.width=8, fig.height=4}
```

```{r msit_dn-cvrt, fig.width=8, fig.height=4}
```

## Associations between RT and phenotypic measures

```{r ftwo}
```

All of these regression analyses were done individually (i.e., each phenotypic measure was associated with RT in an individual/seperate model).

### Incoherent-Coherent (Difference) Trials

```{r select-difference}
```

#### Mean RT

```{r difference-meanrt-totals, fig.width=12, fig.height=6}
```

```{r difference-meanrt-sipi, fig.width=8, fig.height=4}
```

```{r difference-meanrt-erq, fig.width=8, fig.height=6}
```

```{r difference-meanrt-rrs, fig.width=8, fig.height=4}
```

```{r difference-meanrt-panas, fig.width=8, fig.height=6}
```

#### RT CV

```{r difference-cvrt-totals, fig.width=12, fig.height=6}
```

```{r difference-cvrt-sipi, fig.width=8, fig.height=4}
```

```{r difference-cvrt-erq, fig.width=8, fig.height=6}
```

```{r difference-cvrt-rrs, fig.width=8, fig.height=4}
```

```{r difference-cvrt-panas, fig.width=8, fig.height=6}
```

### Coherent Trials

```{r select-coherent}
```

#### Mean RT

```{r coherent-meanrt-totals, fig.width=12, fig.height=6}
```

```{r coherent-meanrt-sipi, fig.width=8, fig.height=4}
```

```{r coherent-meanrt-erq, fig.width=8, fig.height=6}
```

```{r coherent-meanrt-rrs, fig.width=8, fig.height=4}
```

```{r coherent-meanrt-panas, fig.width=8, fig.height=6}
```

#### RT CV

```{r coherent-cvrt-totals, fig.width=12, fig.height=6}
```

```{r coherent-cvrt-sipi, fig.width=8, fig.height=4}
```

```{r coherent-cvrt-erq, fig.width=8, fig.height=6}
```

```{r coherent-cvrt-rrs, fig.width=8, fig.height=4}
```

```{r coherent-cvrt-panas, fig.width=8, fig.height=6}
```

### Incoherent Trials

```{r select-incoherent}
```

#### Mean RT

```{r incoherent-meanrt-totals, fig.width=12, fig.height=6}
```

```{r incoherent-meanrt-sipi, fig.width=8, fig.height=4}
```

```{r incoherent-meanrt-erq, fig.width=8, fig.height=6}
```

```{r incoherent-meanrt-rrs, fig.width=8, fig.height=4}
```

```{r incoherent-meanrt-panas, fig.width=8, fig.height=6}
```

#### RT CV

```{r incoherent-cvrt-totals, fig.width=12, fig.height=6}
```

```{r incoherent-cvrt-sipi, fig.width=8, fig.height=4}
```

```{r incoherent-cvrt-erq, fig.width=8, fig.height=6}
```

```{r incoherent-cvrt-rrs, fig.width=8, fig.height=4}
```

```{r incoherent-cvrt-panas, fig.width=8, fig.height=6}
```
